SIR Model With Testing Flows and Isolation

### 2021-01-18 codes/sir_macpan.Rnw
forcast updated

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
## Forecasting
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
## Here, an example involving changing the transmission rate ($\beta$) in the future due to lockdown ...

## Goal: to forcast after the date of lockdown
lockdown <- as.Date("2021-01-14")
enddate_f <- as.Date("2021-01-31") ## for forecasting

>>>>

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
## Forecasting
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
## Here, an example involving changing the transmission rate ($\beta$) in the future due to lockdown

pp <- coef(fitted.mod, "all") # all the fitted params in the form of ICU1
# pp <- fix_pars(params, target = c(R0 = 1.3, Gbar=6)) # or you could specify your R0 and Gbar
state <- make_state(params=pp)

startdate <- as.Date("2020-12-11")
enddate <- as.Date("2021-01-30")

sim0 <- run_sim(pp,state,start_date=startdate,end_date=enddate)
gg0 <- (ggplot(sim0,aes(x=date))
	+ geom_point(aes(y=report))
)
print(gg0)

## Question: the runsim gives reported cases starrting from 2465 cases and grows, it doesn't match the reported data! I think I am missing some scaling here?

## Goal: to forcast after the date of lockdown
## We want a dataframe that includes the time varying relative $\beta$ at relative $\beta$ to drop by a factor of 2 (linearly) between 14 Jan 2021 on at each saved time point.
lockdown <- as.Date("2021-01-14")

time_pars <- data.frame(Date=as.Date(startdate:enddate)
	, Symbol="beta0"
	, Relative_value= pp[["beta0"]] ## Here I am using the caliberated Beta0
)
	# , stringsAsFactors=FALSE)

time_pars2 <- 
    data.frame(Date=as.Date(startdate:enddate)
             , Symbol="beta0"
             , Relative_value = 
                   c(rep(pp[["beta0"]], length(startdate:lockdown)-1)
                   , seq(pp[["beta0"]],pp[["beta0"]]-0.1,length.out = length(lockdown:enddate))
                     )
               )
print(time_pars2)

sim0_t_reduce <- update(sim0, params_timevar=time_pars2)
gg_rel_beta <- (ggplot(time_pars, aes(x=Date))
	+ geom_point(aes(y=Relative_value))
	+ geom_point(data=time_pars2, aes(x=Date, y=Relative_value), color="red")
)
print(gg_rel_beta)
# We can now look at the relative value of $\beta$ in each scenario, and the corresponding forecasted epidemic curves.

print(gg0
		+ geom_point(data=sim0_t_reduce, aes(x=date,y=incidence), color="red")
)
